25 years of Social Work Research

### 2015-03-12 dataCleaning.Rmd
Final cleanup before lockdown.

# Overview

This document summarizes data cleaning procedures of the data file processed by the `ebscoBWR` fucntion.  It should be noted that that `ebscoBWR` function merged the search results from the first- and second-level searches performed on the three databases (psycInfo, Social Science Abstracts, and Social Work Abstract) hosted by the EbscoPlatform.  This function merged all the search results, transformed the data into a structured data file, and removed all duplicate article records.  No further transformations or cleaning was performed by the `ebscoBWR` function.  Provided below are basic descriptive summaries of the results from the full search before further cleaning.

The main file for analysis is `fullDF.R`, and a separate file is just for psycInfo `psycInfoDF.R`.  The same cleaning procedures need to be performed on both data files prior to analysis.

# Initialization of workspace

```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=TRUE}
# Clear workspace
rm(list=ls())

# Load required packages
library(ggplot2)
library(dplyr)

# Read data files

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
```

# Combines EbscoHost and ProQUest

This section ... wrangles and eliminates duplicate article titles

```{r appendData, comment=NA}

#Creates variable with highest article ID from ebscohost database
ebscoIDmax<-max(ebscoBWR.df$articleID)

#Recodes article ID in ProQuest database in advance of merger with ebscohost
proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+ebscoIDmax)

full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
```

```{r reduced, comment=NA}
titles <- filter(full.df, attributes == "article")
journals <- filter(full.df, attributes == "journal")
year <- filter(full.df, attributes == "pubYear")

year.journal <- dplyr::intersect(year$articleID, journals$articleID)
year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)

full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
```

Exclude incorrectly captured articles. 
```{r}
#Identify records that were incorrectly captured in the wrangle
#using regular expressions
insert.1<-"[B|b]ook [R|r]eview[.:]|^[F|f]orum.+|[F|f]orum$|[C|c]ommentary|Comment.+"
insert.2<-"^[I|i]ndex\\s[T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
insert.5<-"[S|s]pecial\\s[I|i]ssue|[T|t]able\\s[O|o]f\\s[C|c]ontent|\\([U|u]ndetermined"
insert.6<-"^Book.+ | ^COMMENTARY.+ | Call\\s.+ | Contents.+ | Editor.+ | Errat.+"
insert.7<-"^FROM\\THE.+ | ^From\\sthe\\ed.+ | Health\\s[&]\\sS.+ | ^LETTER.+ |
             ^Letter\\sfrom.+ | ^News\\and.+ | ^Response\\sto\\s[A-Z] | Vol\\.\\s[0-9] |
            ^Volume.+ | ^\\["
insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, insert.6, 
              insert.7, sep="|")

badRecords<-subset(titles, grepl(insert, record))
badRecords.ID<-badRecords$articleID

full.df <- full.df[!(full.df$articleID %in% badRecords.ID), ]

Duplicate title search
```{r}
titles$matching <- tolower(titles$record)

#Eliminate `the` and `a` at the beginning of sentences and after colons
titles$matching <- gsub("^the\\s", "", titles$matching)
titles$matching <- gsub("^a\\s", "", titles$matching)
titles$matching <- gsub("[[:punct:]]", "", titles$matching)

#Strips out white space and punctuation to ensure small differences in data 
#entry are detected during duplicate elimination
titles$matching <- gsub(" ","", titles$matching)

duplicated.titles <- duplicated(titles$matching)
duplicated.ID <- titles$articleID[duplicated.titles]
full.df <- full.df[!(full.df$articleID %in% duplicated.ID), ]
```

# Data cleaning and pre-processing

## Narrow results to past 25 years

Inspection of the data indicated notable delays in indexing for the years 2014 and 2015.  Therefore, these years were excluded from the current study.  Thus, this study includes journals indexed through the end of 2013.

```{r}
year.25 <- as.character(c(1900:1987, 2014, 2015))

temp.df <- filter(full.df, attributes == "pubYear")

year.remove <- temp.df[temp.df$record %in% year.25, ]
year.removeID <- year.remove$articleID

full.df <- full.df[!(full.df$articleID %in% year.removeID), ]

```{r}
full.df$record <- ifelse(full.df$record == 
    "The British Journal of Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Revista de Asistenta Sociala (Social Work Review)",
        "Social Work Review",
                        full.df$record)

full.df$record <- gsub("Arete", "xxx", full.df$record)
full.df$record <- gsub("Aret.{1,3}", "Arete", full.df$record)
full.df$record <- gsub("xxx", "Arete", full.df$record) 
                                      #Replaces special character       
                                      #in Arete and preserves other formatting

full.df$record <- ifelse(full.df$record ==
    "Journal of Gay and Lesbian Social Services",     #Spelling difference
        "Journal of Gay & Lesbian Social Services",
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Canadian Social Work Review/Revue canadienne de service social",
        "Canadian Social Work Review",
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "INDIAN JOURNAL OF SOCIAL WORK",                    #Spelling difference
        "Indian Journal of Social Work",
                      full.df$record)

full.df$record <- ifelse(full.df$record ==
    "The Indian Journal of Social Work",              #Spelling difference
        "Indian Journal of Social Work",
                            full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Asia Pacific Journal of Social Work",              #Spelling difference
        "Asia Pacific Journal of Social Work and Development",
                            full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Social Work & Society",                           #Spelling difference
        "Social Work and Society",
                            full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Journal of Social Work in Disability & Rehabilitation",
        "Journal of Social Work in Disability and Rehabilitation", 
                            full.df$record)           #Spelling difference

full.df$record <- ifelse(full.df$record ==
    "Hong Kong Journal of Social Work",
        "The Hong Kong Journal of Social Work", 
                            full.df$record)           #Spelling difference

full.df$record <- ifelse(full.df$record ==
    "The Journal of Baccalaureate Social Work",
        "Journal of Baccalaureate Social Work", 
                            full.df$record)           #Spelling difference

full.df$record <- ifelse(full.df$record ==
    "Journal of Practice Teaching in Health and Social Work",
        "Journal of Practice Teaching in Social Work and Health", 
                            full.df$record)           #Spelling difference

full.df$record <- ifelse(full.df$record ==
    "Professional Development: The International Journal of Continuing Social Work Education",
        "Professional Development", 
                            full.df$record)           #Spelling difference

dim(filter(full.df, attributes == "pubYear"))
dim(filter(full.df, attributes == "article"))
dim(filter(full.df, attributes == "journal"))

## Initial descriptive summary

```{r preprocessing, comment=NA, echo=TRUE} 
number.of.articles <- length(which(full.df$attributes == "article"))
range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
```

```{r}
# Number of articles
cat(number.of.articles)
```

```{r}
# Range of years
cat(range.of.years)
```

## Exclusion of journals not meeting supplemental search terms

The search for journals involved a two-stage process.  It began by extracting all records from journals based on the social work journal list of Hodge and L (APA cite).  Journals were excluded if they did not contain one of the major search terms from the supplemental list.  The majority of these journals were captured in the supplemental search query because the journal used one of the supplemental search terms in a special issue.  The mission and scope of journals were also reviewed when it was unclear whether the journal was specific to social work research (e.g., _The Clinical Supervisor_).  The supplemental search terms included:

+ social work
+ social welfare
+ social casework (or social case work)
+ social service
+ human service
+ social development 
+ social environment

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "Professional Development in Education",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "Arete: Revista de Filosofia",
    "Arete Revista de Filosofia")

ebsco.remove <- full.df[full.df$record %in% exclusions.1, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]

rm(ebsco.remove)

```{r preprocessing, comment=NA, echo=TRUE} 
number.of.articles <- length(which(full.df$attributes == "article"))
range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
```

```{r}
# Number of articles
cat(number.of.articles)
```

```{r}
# Range of years
cat(range.of.years)
```

```{r echo=FALSE, comment=NA}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())
print.data.frame(unique.titles, rowNames=FALSE)
```

## Exclusions of social work publications

+ Journals that did not have at least one full year of indexed records (except journals that subsequently changed titles).  This exclusionary criterion was consistent with the working definition of a social work journal.

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Issues in Social Work Education", 
    "Maatskaplike Werk/Social Work",
    "Pediatric Social Work", 
    "Critical Social Work"
    )

ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]

rm(ebsco.remove, exclusions.2)
```

## Fix journal titles

Additional pre-processing was conducted on journal titles to resolve spelling errors or other minor title differences in the database. For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)  We also applied a global substitution of _and_ with _&_, as this was a common source for differences.

```{r echo=FALSE}
full.df$record <- ifelse(full.df$record == 
        "Social Work & Social Sciences Review",     # Spelling difference
        "Social Work and Social Sciences Review", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Social Work with Groups",                  # Spelling difference
        "Social Work With Groups", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Journal of Sociology & Social Welfare",    # Spelling difference
        "Journal of Sociology and Social Welfare",  
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
    "The British Journal Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)

#shortens Professional Development
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub(":.+", "", full.df$record), 
        full.df$record)

#shortens Canadian Social Work review by eliminating foreign title and is
#automatically combined with other short spelling
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub("(/R){1}.+", "", full.df$record), 
        full.df$record)

# shortens Contemporary Rural Social Work
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub("\\s\\(.+", "", full.df$record), 
        full.df$record)

full.df$record <- ifelse(full.df$attributes == "journal", 
      gsub("and", "&", full.df$record), full.df$record)

```{r echo=FALSE, comment=NA}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())
print.data.frame(unique.titles, rowNames=FALSE)
```

## Title merging

Some social work journals changed titles over their history.  For example, _Families in Society_ had three titles that preceded the current title:  _Social Casework_, _Journal of Social Casework_, and _The Family_.  The database that contributed the largest number of articles to the study database indexed the majority of journal titles under the journal's current name, and provided an additional data field for the historical name.  However, historical names from Social Science Abstracts and Social Work Abstracts were not merged with the current name.  Thus, the last step of the data cleaning procedures was to conduct these merges.

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == 
    "The British Journal of Pyschiatric Social Work" | 
        full.df$record == 
    "The British Journal of Social Work", # Old
        "British Journal of Social Work",           # New title
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Computers in Human Services",              # Old title
        "Journal of Technology in Human Services",  # New title
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "The Family" | full.df$record ==                    # Old title
        "Journal of Social Casework" | full.df$record ==    # Old title
        "Social Casework",                                  # Old title
        "Families in Society",                              # New title
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Social Work in Education",                 # Old title
        "Children & Schools",                       # New title
                    full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Journal of Independent Social Work" | full.df$record ==    # New title
        "Journal of Analytic Social Work",                          # Old title
        "Psychoanalytic Social Work",                               # Old title
                full.df$record)

full.df$record <- ifelse(full.df$record ==
        "Journal of Practice Teaching in Social Work and Practice", #Old title
        "Journal of Practice Teaching in Social Work and Health",   #New title
                    full.df$record)

# Journals were originally merged after suffixes were eliminated (after the
# colon).  Thus, Practice: Social Work in Action  (new title) was shortened to
# Practice (old title).  This section resolves two of these issues to be
# consistent in the comparison with Hodge.

practice.temp <- grep("^Practice$", full.df$record)
full.df$record[practice.temp] <- "Practice: Social Work in Action"

practice.temp <- grep("^Reflections$", full.df$record)
full.df$record[practice.temp] <- "Reflections: Narratives of Professional Helping"
```

# Post-processing summary

## Revised database

This section provides a summary of the revised database after the initial processing with the `ebscoBWR` function and the subsequent data cleaning.  An additional code is included in this summary to indicate whether the journal title overlaps with the list of Hodge (indicated by *H*).

@@

final.list <- cbind(n.so.yr, H)

print.data.frame(final.list, row.names=FALSE)
```

# Comparison with Hodge

This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, and _differences_.

## Intersection

This list shows which journal titles are common to both lists.

```{r}
unique.swHistory <- filter(full.df, attributes == "journal") %>%
                distinct(record)

@@

```{r}
print(sort(hodge.swHistory.intersect))
```

@@

This list shows the articles on Hodge but not the current study.

```{r}
print(sort(hodge.swHistory.diff))
```
This list shows the articles on the current study but not on Hodge.

```{r}
print(sort(swHistory.hodge.diff))
```

## Descriptive summary of records

```{r comment=NA, echo=TRUE} 
number.of.articles <- length(which(full.df$attributes == "article"))
range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
```

```{r}
# Number of articles
cat(number.of.articles)
```

```{r}
# Range of years
cat(range.of.years)
```

```{r}
cor.data <- select(final.list, first, last, n) %>%
            mutate(no.years = as.numeric(last) - as.numeric(first))

ggplot(cor.data, aes(x = no.years, y = n)) + 
            geom_point(shape = 1) + 
            geom_smooth() + 
            xlab("Years") + 
            ylab("Number of articles")

cor(cor.data$no.years, cor.data$n)
```

The following evaluation argument in the chunk is set to FALSE.  Set this function to TRUE to process CSV files of the target journals for inspection. CSV files are named by the journal title.  Be sure to use the exact spelling of the journal as it is contained in the data files.  Set the other arguments to TRUE if you want additional fields to be included.  Please note that it will save the files to your current working directory, which is not specified in this Markdown document.

```{r eval=FALSE}
journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
                           authorAff = FALSE, abstract = FALSE){
    article.search <- which(full.df$record == journalTitle)
    article.search <- full.df[article.search,]
    article.search.ID <- select(article.search, articleID)
    target.ID <- full.df$articleID %in% article.search.ID$articleID
    journal.article.df <- full.df[target.ID, ]
    if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
    if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
    if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
    x.shortened <- gsub(" ", "", journalTitle)
    write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
    }

journalArticleFinder.f("Research on Social Work Practice")
journalArticleFinder.f("Social Work")

>>>>

`r knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, comment=NA)`

```{r initialization_dataprocessing}
rm(list=ls())   
# Load required packages
library(ggplot2)
library(dplyr)

# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)

# Load special functions
source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")

pretty <- function(x){
    x <- prettyNum(x,big.mark=",",scientific=F)
    x
    }
```

```{r appendData, comment=NA, echo=FALSE}
appendData.f()

append.articles <- length(which(full.df$attributes == "article"))
append.journals <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())
```

```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE}
shortArticles.f()
```

```{r titleMatching, echo=FALSE}
titleMatching.f()

articles.titleMatching <- length(which(full.df$attributes == "article"))

journals.titleMatching <- filter(full.df, attributes == "journal") %>%
        summarise(Unique = n_distinct(record))
```

```{r otherDocuments, echo=FALSE}
otherDocuments.f()
articles.otherDocuments <- length(which(full.df$attributes == "article"))
journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r final, comment=NA, echo=FALSE}
fewArticles.f()
articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

# Methods

### Extraction of article records

Our list of social work journals was guided by the work of Hodge and Lacasse (2011).  More specifically, Hodge and Lacasse (2011) identified 84 disciplinary social work journals based on a variety of sources, including _An Author’s Guide to Social Work Journals_ (NASW Press, 1997), Thyer’s (2005) more recent listing of social work periodicals, and Genamics JournalSeek (http://journalseek.net/). Hodge and Lacasse (2011) examined the mission and aims of each journal, and eliminated journals that were specific to another field or had an had an inter-disciplinary focus.  For the current study, our primary search query included all journal titles in this list.

To help ensure comprehensive coverage of all possible core social work journals, we created a supplemental search query that extracted journal titles with any of the following terms:

+ "social work"
+ "social welfare"
+ "social casework"
+ "social service" 
+ "human  service" 
+ "social development" 
+ "social environment"

Using this search queries, we extract journal article recrods from three major databases on the EbscoHost platform:  PsycINFO, Social Service Abstracts, and Social Work Abstracts.  Because of known gaps in indexing in databases (Holden, Barker, Kuppens, Rosenberg & LeBreton, 2014; Holden, Barker, Covert-Vail, Rosenberg, & Cohen, 2009), we also searched ProQuest, which linked to an additional 46 minor databases, including (but not limited to): ERIC, Sociological Abstracts and Worldwide Political Science Abstracts.  In every search, we used a filter in attempt to extract only article records that were classified as _journal articles_, thereby excluding other forms of scholarly communication that was not relevant to the current study (e.g., book reviews, editorials, obituaries, etc.).  We limited the timeframe to a 25 year period, from 1988 to 2013 (inclusive).  Articles published in years 2014 and 2015 were excluded because of delays in indexing.  Search results were exported in batches of article records based on the restrictions of the platform.  Article records were text files in a _generic bibliographic format_.  The article records contained various meta-data based on the database from which the article record was extracted.   Meta-data include (but are not limited to):  article title, journal title, publication year, author name(s), author affiliation(s), abstract, keywords, methodological classification, funding source, location of study, subject groups, digital object identifier (DOI), number of references, number of pages, etc.  These files were post-processed into a structured database using a set of scripts written in the R statistical programming language.  The initial search resulted in 36,094 article records from 117 different journals.

The search queries were purposefully specified to be overly inclusive to ensure full coverage of all possible social work journals contained in the major and minor databases.  Additionally, a visual inspection of the article records revealed problems in the original indexing of articles that requires subsequent data cleaning.  Thus, our data cleaning procedures focused separately on journal titles and article records.

### Data cleaning: Journal titles

The first step of data cleaning involved fixing journal title names due to discrepant errors in indexing. For example, _Journal of Gay and Lesbian Social Services_ was indexed as a journal separate from _Journal of Gay & Lesbian Social Services_ (use of "and" vs. "&").  Other examples involved journals indexed with and without subtitles, or journals with and without the word "The" at the beginning of the title.  Additionally, some journals changed titles over their history.  For example, _Journal of Technnology in Human Services_ is formerly known as _Computers in Human Services_.  In these situations, the former titles were merged with the current titles.

Many journals from allied health disciplines used one of the supplemental search terms in special editions, which were also included in the journal title.  Thus, many non-social work journals were captured in the extraction process.  To resolve this issue, we created a list of all journal titles that were not part of the core list defined by Hodge and Lacasse (2011).  Study authors reviewed these journal titles and discussed whether each candidate title should be retained or excluded.  When disagreements occurred, the study authors reviewed the mission and aims of the journals, names of editorial board members, and focus of the articles.  A consensus was reached on all journal titles to be excluded and retained.   After these procedures, the number of article records and journal titles was reduced to `r pretty(append.articles)` and `r append.journals` (respectively).

### Data cleaning:  Article records

Our search procedures involved the use of three major databased and 46 minor databases, which resulted in some duplication of article records.  Thus, a matching algorithm was constructed to identify and remove all duplicate article records. As previously noted, the filtering of only journal articles was not successful due to errors in the original indexing.  Thus, other scholarly communications were captured in the extractio process.  These other scholarly communications were readily identified due to specific patterns in the titles, such as the terms "Book Review," "From the Editor," and "Obituary."  Given the number of article records in the database, it was not feasbile to manually extract these recrods.  Instead, we created a separate database with representative examples of article records that we wanted to extract.  We also added representative examples of article records to be retained.  We then wrote a series of _regular expressions_ to extract the problematic article records.  Regular expressions are a sequence of characters that form search patterns, allowing extraction of records that match the specified pattern.  In other words, it is a more sophisticated implementation of the search function common to all major word processors.  We tested our regular expressions on the test database, achieving > 95% accuracy with regard to retaining and extracting article records.  These regular expressions were then applied to the full database.  We then excluded article records if they were missing essential meta-data, including author name(s), journal title, article title, and publication field.  As an additional requirement, we required all articles to be $\geq 3$ pages in length.   Finally, we eliminated all social work journals with total article counts of < 10 for the enitre 25 year window (_Issues in Social Work Education_, _Maatskaplike Werk/Social Work_, _Pediatric Social Work_, and _Critical Social Work_).  These cleaning procedures resulted in a final database of `r pretty(articles.final)`  and `r journals.final`.

### Data quality checks

We performed a variety of checks on the final database.  Because the size of the database, it was not feasible to manually inspect all records.  Thus, we randomly sampled article records from the database and cross-checked the data we procured with the information listed with the journal's homepage.  We also inspected a scatter plot of the number of article records for each journal by the number of years the journal appeared within the 25 window timeframe.  Journals that exhibited significant deviation from the regression line were inspected to ensure that our cleaning procedures did not systematically exclude article records or retain other scholarly communications.  All observed discrepancies were verified as differences in journals actual publication output.  Finally, we also made checks of number of journal article records for various journals indexed in the _Web of Science_.  Although the counts were close -- i.e., within 10% -- similar indexing problems observed from our record extraction were also observed in the _Web of Science_ database, such as misclassification of book reviews as journal articles.  Thus, we are unable to quantify the actual amount of error in our database is due to problems in indexing.  At the same time, we are relying on the same source of data that social work researchers use to inform their work.  Too much cleaning and post-processing of the search results can give rise to validity issues because social work researchers are using an information source that contain the errors we have attempted to eliminate.  The issue of reliability and validity are given further attention in the discussion section of this study.

\newpage

@@

final.list <- cbind(n.so.yr, H)
print.data.frame(final.list, row.names=FALSE)

\newpage

```{r message=FALSE, warning=FALSE}
cor.data <- select(final.list, first, last, n) %>%
            mutate(no.years = as.numeric(last) - as.numeric(first))

ggplot(cor.data, aes(x = no.years, y = n)) + 
            geom_point(shape = 1) + 
            geom_smooth() + 
            xlab("Years") + 
            ylab("Number of articles")
```

\newpage

```{r intersection}
unique.swHistory <- filter(full.df, attributes == "journal") %>%
                distinct(record)

@@

@@

Articles on Hodge and Lacasse (2011) but not in the current study.

```{r}
print(sort(hodge.swHistory.diff))
```

```{r eval=FALSE}
journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
                           authorAff = FALSE, abstract = FALSE){
    article.search <- which(full.df$record == journalTitle)
    article.search <- full.df[article.search,]
    article.search.ID <- select(article.search, articleID)
    target.ID <- full.df$articleID %in% article.search.ID$articleID
    journal.article.df <- full.df[target.ID, ]
    journal.article.df <- filter(journal.article.df, attributes == "article")
    journal.article.df <- arrange(journal.article.df, record)
    if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
    if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
    if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
    x.shortened <- gsub(" ", "", journalTitle)
    write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
    }

journalArticleFinder.f("Journal of Gerontological Social Work")
#journalArticleFinder.f("Social Work")
